\documentclass[a4paper,12pt]{letter}

\usepackage{times}
\usepackage{fullpage}
\usepackage{nopageno}
\usepackage[usenames,dvipsnames]{color}

\begin{document}

\begin{center}
\textbf{\Huge Wenliang Li} \linebreak

\textrm{\normalsize	7-2-201, No 7 Kelamayi West Road} \linebreak
\textrm{\normalsize Urumqi, Xinjiang, China 830000} \linebreak
\textrm{\normalsize Tel: 0086-991-4820026} \linebreak
\textrm{\normalsize E-mail: wenliang.billlee@gmail.com} \linebreak
\textrm{\normalsize Personal Website: www.billlee.co.cc}
\end{center}

%\raisebox{0pt}[0pt][0pt]{
%\raisebox{-5ex}{\textbf{\Large Profile}}
%}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Profile}}}

\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize A responsible and patient person with wide experiences of living and studying abroad. Able to learn from mistakes. A consistent work and good team player with effective communication skills, good at forward planning and logic thinking, enjoy working in laboratory. Excellent programing skills, a fast learner.}
\end{itemize}

%\textbf{\Large Academic Achievement \hspace{20cm}} \linebreak
%\rule[0.3cm]{10cm}{.1pt}
%\begin{itemize}
%\item \textrm{\normalsize Achieved the distinction grade for the first academic yeat in University of Kent.}
%\item \textrm{\normalsize Achieved adequate marks in second and third academic year to be allowed continue the forth year of M-physics degree.} 
%\end{itemize}
%\vspace{0.5cm}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Computing Skill}}}
 
\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize Operating System: Linux, Macintosh, Windows.}
\item \textrm{\normalsize Program Scripting: C++, Fortran 90, BASH.}
\item \textrm{\normalsize Data ploting: ROOT, IDL, SPLASH.}
\item \textrm{\normalsize Word Processing: Latex, Office.}
\item \textrm{\normalsize Website Building: HTML, CSS.}
\item \textrm{\normalsize Accessory: SVN, FFMPEG, GIMP, Alpine, Dia.}
\item \textrm{\normalsize Some knowledge on network administration and security.}
\item \textrm{\normalsize Experience on website building and maintaining.}
\end{itemize}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Training in Physics}}} 

\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize Electromagnetism and Optics.}
\item \textrm{\normalsize Particle and Nuclear Physics.}
\item \textrm{\normalsize Theoretical Mechanics.}
\item \textrm{\normalsize Quantum Mechanics.}
\item \textrm{\normalsize Statistical Mechanics.}
\item \textrm{\normalsize Solid State Physics.}
\item \textrm{\normalsize Astrophysics.}
\end{itemize}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{History of Study}}} 

\rule[-0.5cm]{10cm}{1pt}

\vspace{2mm}
\textbf{\normalsize ~University of Kent at Canterbury(UK), August 2008 - June 2009}
\begin{itemize}
\item \textrm{\normalsize Carrying out a six month final year project, titled \lq Investigation of the shock-wave velocity in H$_2$ region caused by FUV radiation\rq, as well as taking advanced level lectures. Expected to be graduated by July 2009.} 
\item \textrm{\normalsize Valenteered to be peer mentoring tutor.}

\end{itemize}

\textbf{\normalsize ~Karlsruhe Institute of Technology (Germany), June 2009 - September 2009}
\begin{itemize}
\item \textrm{\normalsize During 3 month long intern-ship in KIT at Germany, I was working for the world largest hybrid experiment for cosmic ray detection, the Pierre Auger Experiment. The work was targeted to develop the algorithm of identifying the miss cabled Photo Multiplier Tube of the florescences telescope. The algorithm makes use of star image detected, and it is proved to be successful.}
\item \textrm{\normalsize In the mid point of intern-ship, I was invited to attend the KIT Summer Institute, and heard dozens of valuable leictures on cutting edge technology and experiment.}
\end{itemize}

\textbf{\normalsize ~University of Penn State (USA), August 2008 - May 2009}

\begin{itemize}
\item \textrm{\normalsize Carrying out a year abroad studying program at University of Penn state.}
\item \textrm{\normalsize Constant member of Society for Physics Students. Valenteered to be peer mentoring tutor.}
\end{itemize}

\textbf{\normalsize ~University of Kent at Canterbury (UK), September 2006 - June 2008}
\begin{itemize}
\item \textrm{\normalsize Assigned with the 4 year M-Physics degree program: Physics with Astrophysics with one year in USA. Successfully completed the first and second academic year.}
\item \textrm{\normalsize Constant member of Astronomy Club.}
\end{itemize}

\textbf{\normalsize ~Loughborough College (UK), September 2002 - June 2006}
\begin{itemize}
\item \textrm{\normalsize Studied English Language Course and A-Level program.}
\end{itemize}

\textbf{\normalsize ~Urumqi No.81 Middle School (China), September 1998 - June 2002} 


\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Qualification}}} 

\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize A-Level Mathematics and Further Mathematics.}
\item \textrm{\normalsize A-Level Physics.}
\item \textrm{\normalsize IETLS Score: 6.0.}
\end{itemize}
\vspace{5cm}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Language Skill}}} 

\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize English (Academic Level).}
\item \textrm{\normalsize Chinese.}
\end{itemize}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Additional Information}}} 

\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize Driving License from CHINA.}
\item \textrm{\normalsize Citizen Ship: Chinese.}
\item \textrm{\normalsize No Tobacco and Alcohol Consumption.}
\end{itemize}
\vspace{0.5cm}

\end{document}



