\documentclass[a4,12pt]{letter}
\usepackage{times}
\usepackage{fullpage}
\usepackage{nopageno}

\signature{Wenliang Li}
\address{69 Tenterden Drive \\ Canterbury \\ Kent \\ UK CT2 7BH}

\begin{document}

\begin{letter}{XXXXX \\ XXXXX \\ XXXXXXXX \\ XXXXXXXX \\ XXXXXXx}
\opening{Dear Madam or Sir:}

I am writing to apply for the Ph.D position in Fundemental Physics Group at Chalmers Institute of Technology starts at 2010. I have enclosed my Curriculum Vitea, academic status letter, transcript and 3 sets of recommandation letter for your review. 
As you may see in my CV, I am a final year M-Physics with Astrophysics student at University of Kent in England. My research interests has always been theoretical particle physics, and the ultimate desire is to seek the fundemental priciple of science. It is delight to accknoledge the similar objective is shared by your group.   

I rate myself as a consitent and causious teamplayer, hold effective communication skills and keen on planning ahead. Despite being a physics student, it is also my interest to explore the subject of computer programming. I am capable of writing computer code for verious perpuses in either C++, Perl or Python. Good linux operating ability enables me to fulfill any tasks, such as website building, world processing, image manipulation, aminimation etc. I strongly believe my exellent programming skill will be the biggest impacting factor I can offer to the group. 

I have had two optunities to perform real life research:
\begin{itemize}
\item 3 month internship at Karlsruhe Institute of Technology (KIT) in 2009. 
\item 6 month final year M-Physics project, is curretly under-going.
\end{itemize}
More details about two research programs can be found in my CV and letters of recommandation.

Over the period of being a student, I have been spending considerable amount of time on collecting and analysing academic material and teaching technique. Uniquely, majority of leictures were voice recorded, in preperation of leicturing student in the near future. In past two years, I offered myself as peer mentoring tutor, and enjoyed experience very much. 

With more than 8 years of studying and living abroad, I managed to survie four different countries and met many intellectuals. A big advantage of mine is the ability to adapt into the new working and living enviroment for a short period of time. Never the less, internation expericence may also bring benefit to the group.

A language course in Swedish is one of the attempting offer from Chalmers. Not only I will be trained to speak the third language, but also be given a chance to explore and understand a different culture. The Sweedish experience ahead could be the opptunity to fill my multi-national personality with Skandinavian character.

I would be grateful if I can be given a chance to an interview. Thank you for your consideration. I look forward to your reply.

\closing{Yours Faithfully,}

\end{letter}
\end{document}
