\documentclass[12pt, letterpaper]{letter}

\usepackage{times}
\usepackage{fullpage}

\signature{Wenliang Li}

\address{Wenlaing Li \\175 Deergrove Cre \\ Regina, SK, S4S 5M2}
\begin{document}
 
\begin{letter}{U.S. Consulate\\ 615 Macleod Trail, S.E. \\ Calgary, Albert, T2G 4T8}

\opening{Dear Madam/Sir:}
I am writing to apply for the B-1 type visa for the trip to Thomas Jefferson National Accelerator Facility (Jlab) in Virginia, USA. I am currently a Master of Science student in Department of Physics at University of Regina, Canada. My research in conducted under the supervision of Dr.Grath Huber who has over 20 years of research experience associates with Jlab. For research purposes, I need to attend 2-3 collaboration meetings per year and specialized workshop (2-3 times per year) through to the end of 2013. All my expenses will be covered by University of Regina and insurance is covered by Jlab.

Previously I was in Pennsylvania State University for one year exchange as student from British Institute. 

In order to support my application, I have enclosed the following documentations for further review:
\vspace{-5mm}
\begin{enumerate}
	\item Invitation Letter from Jlab Hall C Group Leader
	\item Endorsement Letter from Dr. Garth Huber 
	\item Position Appointment Letter from University of Regina
	\item Canadian Student Visa and Study Permit
	\item Curriculum Vitae
	\item Statement of My Research
	\item Transcript from University of Kent and Pennsylvania State University
	\item Expired US Student Visa from 2009
\end{enumerate}
\vspace{-2mm}

Many thanks for your consideration, and I am looking forward to hearing from you.

\closing{Yours Faithfully,}
 
\end{letter}
\end{document}

