\documentclass[a4paper,12pt]{letter}

\usepackage{times}
\usepackage{fullpage}
\usepackage{nopageno}
\usepackage[usenames,dvipsnames]{color}

%\usepackage{paralist}


\usepackage{multienum}

\usepackage{shortlst }


\begin{document}



\newcommand{\secb}{ ~\\[-15mm]}

\newcommand{\parab}{ ~\\[-8mm]}


%****************************************
% Permenant address
%
% \begin{center}
% \textbf{\Huge Wenliang Li} \linebreak
% 
% \textrm{\normalsize	7-2-201, No 7 Kelamayi West Road} \linebreak
% \textrm{\normalsize Urumqi, Xinjiang, China 830000} \linebreak
% \textrm{\normalsize Tel: 0086-991-4820026} \linebreak
% \textrm{\normalsize E-mail: wenliang.billlee@gmail.com} \linebreak
% \textrm{\normalsize Personal Website: www.billlee.co.cc}
% \end{center}
%****************************************

\begin{center}
\textbf{\Huge Wenliang Li} \\[3mm]
\textrm{\normalsize 175 Deergrove Cre, Regina} \linebreak
\textrm{\normalsize SK, Canada. S4S 5M2} \linebreak
\textrm{\normalsize Tel: 1-306-5854653} \linebreak
\textrm{\normalsize E-mail: wenliang.billlee@gmail.com} \linebreak
\textrm{\normalsize Personal Website: www.billlee.co.cc}
\end{center}

~\\[-20mm]

%\raisebox{0pt}[0pt][0pt]{
%\raisebox{-5ex}{\textbf{\Large Profile}}
%}

%/*--------------------------------------------------
% Profile
\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Profile}}}
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize A responsible and patient person with wide experiences of living and studying abroad. Able to learn from mistakes. A consistent worker and good team player with effective communication skills, good at forward planning and logic thinking, enjoy working in laboratory. Adequate programing skills, a fast learner.}
\end{itemize} 

\secb

%/*--------------------------------------------------
% History of Study

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{History of Study}}} 
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}

\vspace{2mm}

\textbf{\normalsize ~University of Regina (Canada), September 2010 - September 2012 (Expected)} \\[-8mm]
\begin{itemize}
\item \textrm{\normalsize Master of Science in Physics student, on construction of the Heavy Gas Cerenkov detector, to be installed on the Super High Momentum Spectrometer at Jefferson Lab Hall C.  This work is performed under the supervision of Dr. Garth Huber. Teaching Assistant for first year physics classes.}  
\end{itemize}

\textbf{\normalsize ~University of Kent at Canterbury (UK)} \\[-8mm]
\begin{itemize}
\item \textrm{\normalsize Received 4 Year Physics and Astrophysics with year in USA Hon MPhys Degree, with Upper Second overall grade. Carried out six month final year theoretical astrophysics project, titled \lq Investigation of Shock-wave Velocity in H$_2$ Region Caused by FUV Radiation\rq, this work was under the supervision of Dr. Jingqi Miao.} 
\end{itemize}

\textbf{\normalsize ~Karlsruhe Institute of Technology (Germany), June 2009 - September 2009} \\[-8mm] 

\begin{itemize}
\item \textrm{\normalsize During 3 month DAAD intern-ship at KIT in Germany, I worked under the supervision of PHD Student Steffan Mueller, for the world largest hybrid experiment for cosmic ray detection, the Pierre Auger Experiment. This work was targeted to develop the algorithm of identifying the miss cabled Photo Multiplier Tube of the florescences telescope. The algorithm makes use of star image detected, and it is proved to be successful.}
\item \textrm{\normalsize Also attended Particle Physics Summer Institute held at KIT, which covered topics on cutting edge technology and experiment in particle physics.}
\end{itemize}

\textbf{\normalsize ~Pennsylvania State University (USA), August 2008 - May 2009}  \\[-8mm] 

\begin{itemize}
\item \textrm{\normalsize Carried out a year abroad studying program at Pennsylvania state University as part of University of Kent degree requirements.}
%\item \textrm{\normalsize Constant member of Society for Physics Students. Volunteered to be peer mentoring tutor.}
\end{itemize}

\textbf{\normalsize ~University of Kent at Canterbury (UK), September 2006 - June 2008}  \\[-8mm] 
\begin{itemize}
\item \textrm{\normalsize Assigned with the 4 year M-Physics degree program: Physics with Astrophysics with one year in USA. Successfully completed the first and second academic year.}
\item \textrm{\normalsize Constant member of Astronomy Club.}
\end{itemize}

\textbf{\normalsize ~Loughborough College (UK), September 2002 - June 2006}  \\[-8mm] 
\begin{itemize}
\item \textrm{\normalsize Studied English Language Course and A-Level program.}
\end{itemize}

\textbf{\normalsize ~Urumqi No.81 Middle School (China), September 1998 - June 2002} \\[-8mm] 


\vspace{3mm}



\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Referenced Publications}}}
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}

\vspace{2mm}

\textbf{\normalsize ~Collaboration and Technical Reports} \parab
\begin{description}
\item[~2012] \textrm{\normalsize \emph{Heavy Gas \v{C}erenkov Mirror Reflectivity Measurements}, Jefferson lab Hall C collaboration, HallC-doc-\#735-v1, 2012. }
\item[~2012] \textrm{\normalsize \emph{Mirror Testing Result}, Jefferson lab Hall C collaboration, HallC-doc-\#716-v2, 2012. }
\item[~2011] \textrm{\normalsize \emph{Progress Report on Heavy Gas Cerenkov Detector Construction}, Jefferson lab Hall C collaboration, HallC-doc-\#695-v1, 2012. }
\item[~2011] \textrm{\normalsize \emph{Radius of Curvature Measurement of Test Mirror from Sinclair Glass}, Jefferson lab Hall C collaboration, HallC-doc-\#693-v1, 2011.}
\end{description}



\textbf{\normalsize ~Presentations at Workshops and Conferences } \parab
\begin{description}
%\begin{itemize}
\item[~2012] \textrm{\normalsize Hall C SHMS Detector Working Group Meeting, \emph{HGC Mirror Reflectivity Measurement}. }
\item[~2012] \textrm{\normalsize Canadian Association of Physicists Congress, University of Calgary, \emph{Heavy Gas \v{C}erenkov Detector for Jefferson Lab Hall C}. }
\item[~2011] \textrm{\normalsize Hall C SHMS Detector Working Group Meeting, University of Regina Graduate Student's Association Conference, \emph{Particle Identification and Heavy Gas Cerenkov Detector}.}
%\end{itemize}
\end{description}



\secb

%\textbf{\Large Academic Achievement \hspace{20cm}} \linebreak
%\rule[0.3cm]{10cm}{.1pt}
%\begin{itemize}
%\item \textrm{\normalsize Achieved the distinction grade for the first academic yeat in University of Kent.}
%\item \textrm{\normalsize Achieved adequate marks in second and third academic year to be allowed continue the forth year of M-physics degree.} 
%\end{itemize}
%\vspace{0.5cm}

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Computing Skill}}}
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}

% Additional information
% \raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Additional Information}}} 
% 
% \rule[-0.5cm]{10cm}{1pt}
% \begin{itemize}
% \item \textrm{\normalsize Driving License from China.}
% \item \textrm{\normalsize Citizen Ship: Chinese.}
% \item \textrm{\normalsize No Tobacco and Alcohol Consumption.}
% \begin{itemize}
% \item \textrm{\normalsize Operating System: Linux, Macintosh, Windows.}
% \item \textrm{\normalsize Program Scripting: C++, Fortran 90, BASH.}
% \item \textrm{\normalsize Data ploting: ROOT, IDL, SPLASH.}
% \item \textrm{\normalsize Word Processing: Latex, Office.}
% \item \textrm{\normalsize Website Building: HTML, CSS.}
% \item \textrm{\normalsize Accessory: SVN, FFMPEG, GIMP, Alpine, Dia.}
% \item \textrm{\normalsize Some knowledge on network administration and security.}
% \item \textrm{\normalsize Experience on website building and maintaining.}
% \end{itemize}

\begin{itemize}
\item \textrm{\normalsize Data Analysis Framework: ROOT, PHYSICA.}
\item \textrm{\normalsize Experimental Simulation: GEANT 4.}
\item \textrm{\normalsize Computational Language: BASH, C++, PYTHON, PERL, PHP.}
\item \textrm{\normalsize Familiar with linux system maintenance (Debian \& Redhat based distributions).}
\end{itemize}

\secb


\pagebreak

\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Qualification}}} 
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}
\begin{itemize}
\item \textrm{\normalsize Master in Science, expected to graduate in September, 2012 (University of Regina, Canada).}
\item \textrm{\normalsize 4 Year Physics and Astrophysics with year in USA Hon MPhys Degree (University of Kent at Canterbury, UK).}
\end{itemize}

\secb


%\pagebreak

%****************************************
% Language Skille
\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Language Skill}}} 
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}

% \begin{itemize}
% \item \textrm{\normalsize English (Academic Level).}
% \item \textrm{\normalsize Chinese.}
% \end{itemize}
% 

\begin{shortitemize}
\item \textrm{\normalsize English (Academic Level)}
\item \textrm{\normalsize Chinese}
\end{shortitemize}
\secb



%****************************************
% Additional information
\raisebox{0pt}[0pt][0pt]{\Large\textbf{\raisebox{-3.5ex}{Additional Information}}} 
\\[2mm]
\rule[-0.5cm]{10cm}{1pt}

%\begin{itemize}
% \item \textrm{\normalsize Driving License from China.}
% %\item \textrm{\normalsize Citizen Ship: Chinese.}
% \item \textrm{\normalsize No Tobacco Consumption.}
% \end{itemize}

% \begin{multienumerate}
% \mitemxxx{Not}{Linear}{Not}
% \end{multienumerate}

\begin{shortitemize}
\item \textrm{\normalsize Driving License from China.}
\item \textrm{\normalsize No Tobacco Consumption.}
\end{shortitemize}

\secb
%\sb

%****************************************


\end{document}



