\documentclass[12pt, letterpaper]{letter}

\usepackage{times}
\usepackage{fullpage}
\usepackage{nopageno}

%\special{papersize=8.5in,11in}
\usepackage[letterpaper]{geometry}

\signature{Wenliang Li}
\longindentation=0pt

\address{Wenliang Li \\175 Deergrove Cres.\\ Regina, SK, S4S 5M2}
\begin{document}
 
\begin{letter}{Name \\ Address \\ Zipcode}

\opening{Dear Madam/Sir:}

I am writing to apply for the particle physics Ph.D. position in your research group. I have enclosed my Curriculum Vitae, statement of research interests, academic transcript, and 2 sets of recommendation letter for your review

As you may notice from my CV, I am master student at University of Regina Canada, and expected to complete the degree program in September, 2012. Due to the graduation, I am currently seeking for a Ph.D. position in experimental particle physics. The motivation can be found in statement of research interests.

I have had several past research experiences: 

%\vspace{-5mm}
\begin{description}
	\item[~2011] Two year Master research project at University of Regina in Canada.
	\item[~2010] Six month final year M-Physics project at University of Kent at Canterbury in UK.
	\item[~2009] Three month internship at Karlsruhe Institute of Technology (KIT) through DAAD Rise scholarship in Germany.
\end{description}
\vspace{-2mm}

Details of my past research projects can be found in CV and personal statement.

I rate myself as a consistent and cautious team player, hold effective communication skills and keen on planning ahead. Despite being a physics student, it is also my interest to explore computer programing and maintenance. Fore more than 10 tears of the studying and living abroad, I managed to survive five countries in three continents. Thus, one of my biggest advantages is the ability to adapt into the new working and living environment in short period of time. Never the less, my international experience may be beneficial to the group.

I would be grateful if I could be offered an opportunity yo work under your instruction. Thank you for the consideration, I am looking forward yo your reply.

\closing{Yours Faithfully,}
 



\end{letter}
\end{document}

